### 2017-04-06 writing/paper/sections/meshpatterns.tex
Do most of Henning's changes
- Change makefile to output to pdf
- Never need compositions of boksall, so removed.
- fixed consistency with av brackets (I hope)
- fixed Henning  using dollar signs in his edits
- changed Henning's long-form cite to nice automatic textcite
- removed duplicate line about considering as set partitions
Results of Discussions with Henning
- Changed example to be about subpatterns, may need more words
- Removed second description of one example

\begin{example}
    The pattern \(p=\mperm{2,1,3}{\{(0,1),(0,2),(1,0),(1,1),(2,1),(2,2)\}}=
    \textpattern{}{ 2, 1, 3 }{ 0/1, 0/2, 1/0, 1/1, 2/1, 2/2 }\) is contained in
    \(\pi = \perm{3,4,2,1,5}\) but is not contained in \(\sigma = \perm{4,2,3,1,5}\).
\end{example}

@@

TODO: I changed a symbol in the above definition. See the comment.
% if \(\kappa\) contains \(\tau\)
% to
% if \(\kappa\) contains \(p\)
% that is what we want right?

TODO: Change the following example to an example of a mesh pattern in a mesh
pattern.

Now we consider the plot for the permutation \(\sigma\). This permutation
avoids \(p\) since for every occurrence of the classical pattern \(\perm{2,1,3}\)
there is at least one point in one of the shaded boxes. For example, consider the
subsequence \(315\) in \(\sigma\), this is an occurrence of \(\perm{2,1,3}\) but
not the mesh pattern since the points with values \(4\) and \(2\) are in the
regions corresponding to the boxes \(\boks{0,1}\) and \(\boks{0,2}\), which are shaded in
\(p\). This is shown in the plot below.

\begin{equation*}
    \pattern{3,4,5}{4,2,3,1,5}{0/1,0/2,0/3,0/4,
                               1/1,1/2,1/3,1/4,
                               2/1,2/2,2/3,2/4,
                               3/0,3/1,3/2,
                               4/1,4/2,4/3,4/4}
\end{equation*}
This is true for all occurrences of \(\perm{2,1,3}\) in \(\sigma\) and
therefore \(\sigma\) avoids \(p\).

>>>>

\begin{example}
    The pattern \(p=\mperm{2,1,3}{\{(0,1),(0,2),(1,0),(1,1),(2,1),(2,2)\}}=
    \textpattern{}{ 2, 1, 3 }{ 0/1, 0/2, 1/0, 1/1, 2/1, 2/2 }\) is contained in
    \(\pi = \perm{3,4,2,1,5}\).
\end{example}

@@

\begin{example}
    The pattern \(p=\mperm{2,1,3}{\{(0,1),(0,2),(1,0),(2,2)\}}=
    \textpattern{}{ 2, 1, 3 }{ 0/1, 0/2, 1/0, 2/2 }\) is contained in the pattern
    \(r = \textpattern{}{4,2,3,1,5}{0/1,0/2,0/3,0/4,
                               1/0,1/1,1/2,1/3,1/4,
                               2/1,2/2,2/3,2/4,
                               3/2,3/4,
                               4/2,4/3,4/4} \) as a subpattern.
\end{example}

The highlighted points form an occurrence of \(p\) in \(r\)
\begin{equation*}
    \pattern{1,2,5}{4,2,3,1,5}{0/1,0/2,0/3,0/4,
                               1/0,1/1,1/2,1/3,1/4,
                               2/1,2/2,2/3,2/4,
                               3/2,3/4,
                               4/2,4/3,4/4}
\end{equation*}
The permutation \(\perm{4,2,3,1,5}\) also contains \(p\) in the usual sense.
